Results

### 2025-04-02 notebooks/00_index.qmd
update

```{julia}
using Speasy
using Speasy: DataSet
spz = speasy()

using DimensionalData
using SpaceTools
using GLMakie
using Dates
```

```{julia}
tmin = DateTime("2021-04-29")
tmax = DateTime("2021-04-30")

tvars_psp = [
    "cda/PSP_FLD_L2_MAG_RTN_4_SA_PER_CYC/psp_fld_l2_mag_RTN_4_Sa_per_Cyc",
    ["cda/PSP_SWP_SPI_SF00_L3_MOM/DENS", "cda/PSP_FLD_L3_SQTN_RFS_V1V2/electron_density"],
    "cda/PSP_SWP_SPI_SF00_L3_MOM/VEL_RTN_SUN",
    "cda/PSP_SWP_SPI_SF00_L3_MOM/TEMP",
]

tvars_wind = [
    "cda/WI_H2_MFI/BGSE",
    "cda/WI_PM_3DP/P_DENS",
    "cda/WI_PM_3DP/P_VELS",
    "cda/WI_PM_3DP/P_TEMP",
]

f = Figure()
add_title = true
tplot(f[1, 1], tvars_psp, tmin, tmax; add_title)
tplot(f[1, 2], tvars_wind, tmin, tmax; add_title)
add_labels!()
f
```

>>>>

```{julia}
using Speasy
using SPEDAS
using DimensionalData
using GLMakie
# using CairoMakie
using Dates
using PartialFunctions
```

```{julia}
tmin_psp = DateTime("2021-01-14")
tmax_psp = DateTime("2021-01-21")
tmin_wind = DateTime("2021-01-15")
tmax_wind = DateTime("2021-01-23")

tmin_wind = DateTime("2021-01-17")
tmax_wind = DateTime("2021-01-19")

density_tvar = SPEDAS.DataSet(
    "Density",
    [
        "cda/PSP_SWP_SPI_SF00_L3_MOM/DENS",
        "cda/PSP_FLD_L3_RFS_LFR_QTN/N_elec",
        "cda/PSP_FLD_L3_SQTN_RFS_V1V2/electron_density"
    ],
    (title="Density", labels=["SPI", "RFS"])
)

tvars_psp = [
    "cda/PSP_FLD_L2_MAG_RTN_4_SA_PER_CYC/psp_fld_l2_mag_RTN_4_Sa_per_Cyc",
    density_tvar,
    "cda/PSP_SWP_SPI_SF00_L3_MOM/VEL_RTN_SUN",
    "cda/PSP_SWP_SPI_SF00_L3_MOM/TEMP",
]

wind_B = tnorm_combine ∘ SpeasyProduct(
    "cda/WI_H2_MFI/BGSE",
    (; ylabel="B (nT)", labels=["Bx", "By", "Bz", "Magnitude"])
)

wind_vel = tnorm_combine ∘ SpeasyProduct(
    "cda/WI_K0_SWE_RTN/V_RTN"
    # "cda/WI_PM_3DP/P_VELS"
)

tvars_wind = [
    wind_B,
    "cda/WI_PM_3DP/P_DENS",
    "cda/WI_K0_SWE_RTN/V_RTN",
    wind_vel,
    "cda/WI_PM_3DP/P_TEMP",
]

f = Figure(; size=(1200, 800))
add_title = false
# tplot(f[1, 1], tvars_psp, tmin_psp, tmax_psp; add_title)
tplot(f[1, 2], tvars_wind, tmin_wind, tmax_wind; add_title)
add_labels!(; position=Left(), valign=:top, halign=:left, padding=(10, 10, 10, 0));
f
```
